% !TEX root = ../mat999.tex
\newpage
\section{Introduction \label{sec:intro}}
\subsection{Fermat's Last Theorem \label{sec:fermat}}

There are many famous theorems in Mathematics. One of the most famous theorems is Fermat's Last Theorem.

\begin{thm}[Fermat's Last Theorem] \label{thm:fermat}
If $n>2$, there are no integers $a,b,c$ with $abc \neq 0$ such that $a^n + b^n= c^n$.
\end{thm}


% Traditional Mathematics
\subsection{Purpose}

Theorem~\ref{thm:fermat} is one of the most famous theorems in Mathematics. But most undergraduate students do not learn Fermat's Last Theorem. Instead, many students learn formulas such as:
	\[
	\oint_C \mathbf{F} \cdot d\mathbf{r} = \iint_S \nabla \times \mathbf{F} \cdot dS
	\]
But Mathematics starts far more simple than that. The first topic in Mathematics that one typically sees is Arithmetic. For instance, students typically will learn ``FOIL.'' 
	\begin{equation} \label{eq:foil}
	(x + y)^2= x^2 + 2xy + y^2
	\end{equation}
However, \eqref{eq:foil} tends to be a stumbling block for students. Many students will instead claim, incorrectly, that $(x+y)^2= x^2 + y^2$. The purpose of this course will be to prove Dirichlet's Unit Theorem, which states:

\begin{restatable*}[Dirichlet's Unit Theorem]{thm}{unit} \label{thm:unit}
Let $K$ be a number field of degree $n$ with $r$ real embeddings and $s$ conjugate pairs of complex embeddings. Then the abelian group $\O_K^\times$ is a finitely generated abelian group with rank $r+s-1$ and $\O_K^\times \cong \mu_K \times \Z^{r+s-1}$, where $\mu_K$ are the roots of unity in $\O_K$. 
\end{restatable*}


However, it will take some time to prove Theorem~\ref{thm:unit}.